Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
updated ideal poll

The wording of questions should be straightforward and easy to understand, minimizing error in measurement caused by misinterpretation of questions. The question should also be asked neutrally, without leading participants to any particular response. Likert scales, including an option for “don’t know”, should be used for all questions for ease and consistency of participant understanding. As well, keeping questions and answer options simple minimizes the burden placed on participants, which reduces the attrition caused by participants losing interest in the poll [@citeTB]. The “don’t know” option is also effective in helping reduce the decision difficulty to certain participants who are truly unsure. Before officially deploying the survey with our selected sample, it first needs to be tested to catch ambiguous or other poorly phrased questions [@citeTB]. To encourage participation in this research, a financial incentive should be offered for full completion of the poll.

@@

A sample implementation of such poll, created using Google form, can be found [here](https://forms.gle/ti2rjGGVxBukv9dF6). In this version, the order of questions presented is consistent for all respondents due to the limitations of Google form, but for an idealized methodology with more professional surveying platform, such as Survey Monkey, the question order would be randomized when being presented to different respondents with the Question Randomization feature [@surveymonkey]. This will help reduce response order bias, which is when the answer of a question is affected by the order in which it appeared in the survey [@citeStantcheva].

>>>>

The wording of questions should be straightforward and easy to understand, minimizing error in measurement caused by misinterpretation of questions. The question should also be asked neutrally, without leading participants to any particular response. Likert scales, including an option for “don’t know”, should be used whenever possible for ease and consistency of participant understanding. As well, keeping questions and answer options simple minimizes the burden placed on participants, which reduces the attrition caused by participants losing interest in the poll [@citeTB]. The “don’t know” option is also effective in helping reduce the decision difficulty to certain participants who are truly unsure. Before officially deploying the survey with our selected sample, it first needs to be tested to catch ambiguous or other poorly phrased questions [@citeTB]. To encourage participation in this research, a financial incentive should be offered for full completion of the poll. Displaying the progress bar and indicating the survey length at the very beginning also helps encourage participants to complete the full questionnaire. Our poll would also be submitted to the appropriate ethics review boards to increase confidence in our methodology.

@@

A sample implementation of such poll, created using Google form, can be found [here](https://forms.gle/ti2rjGGVxBukv9dF6). In this version, the order of questions presented is consistent for all respondents due to the limitations of Google form, but for an idealized methodology with more professional surveying platform, the question order would be randomized when being presented to different respondents, with consideration for related questions must be kept together. This will help reduce response order bias, which is when the answer of a question is affected by the order in which it appeared in the survey [@citeStantcheva].
